### 2025-06-11 question_papers/aima203_first_in_sem.tex
aima203_question

\question Describe error due to truncation. Find a root of \(f(x)=xe^x-1=0\), correct to \(2\) decimal places. [1+3]

@@

\vspace{4cm}
\question Find a real root of the equation $x^2+y =1, x+y^2=7$, using the method of iteration, correct up-to 2 decimal places. [4]

\question Solve using LU-factorization method. $3x_1 - x_2 = -1, \;\;\; -x_1+3x_2-x_3 = 7, \;\;\; -x_2+3x_3 =7$. [4]
\vskip -5mm
\question Show that the matrix $ \small A=   \begin{bmatrix}
    25  & 24 & 10 \\
    66 & 78 & 37 \\
    92 & -73 & -80
  \end{bmatrix}
  $ is ill-conditioned.
\vspace{12cm}

\question Find a real root of the equation $x^2+y =1, x+y^2=7$, using the method of iteration, correct up-to 2 decimal places. [4]

\question Solve using LU-factorization method. $3x_1 - x_2 = -1, \;\;\; -x_1+3x_2-x_3 = 7, \;\;\; -x_2+3x_3 =7$. [4]
\vskip -5mm
\question Show that the matrix $ \small A=   \begin{bmatrix}
    25  & 24 & 10 \\
    66 & 78 & 37 \\
    92 & -73 & -80
  \end{bmatrix}
  $ is ill-conditioned.
\end{questions}
\end{document}

>>>>

@@

\vspace{4cm}
\begin{questions}
\question Solve using LU-factorization method. $3x_1 - x_2 = -1, \;\;\; -x_1+3x_2-x_3 = 7, \;\;\; -x_2+3x_3 =7$. [4]

\question Determine whether the matrix is ill-conditioned or not.$\small A=   \begin{bmatrix}
    25  & 24 \\
    66 & 78 \\
  \end{bmatrix}$. [2]

\question Using Lagrange's method estimate the value of $y(202)$ from the following data: \\[2mm]
  $(200, 5.2983), (203,5.3132), (206,5.3278), (210,5.3471)$. [4]
  \vspace{12cm}

 \question Solve using LU-factorization method. $3x_1 - x_2 = -1, \;\;\; -x_1+3x_2-x_3 = 7, \;\;\; -x_2+3x_3 =7$. [4]

\question Determine whether the matrix is ill-conditioned or not.$\small A=   \begin{bmatrix}
    25  & 24 \\
    66 & 78 \\
  \end{bmatrix}$. [2]

\question Using Lagrange's method estimate the value of $y(202)$ from the following data: \\[1mm]
  $(200, 5.2983), (203,5.3132), (206,5.3278), (210,5.3471)$. [4]

\end{questions}
\end{document}

%%% Local Variables:
%%% mode: LaTeX
%%% TeX-master: t
%%% End:
